\documentclass[12pt,reqno]{amsart}
\usepackage[top=1.5cm, left=1.5cm,right=1.5cm,bottom=1.5cm]{geometry}
\renewcommand{\baselinestretch}{1.2}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{color,hyperref,enumerate,multicol}
\definecolor{darkblue}{rgb}{0.0,0.0,0.3}
\hypersetup{colorlinks,breaklinks,
            linkcolor=darkblue,urlcolor=darkblue,
            anchorcolor=darkblue,citecolor=darkblue}
\usepackage{tikz}
\usepackage{scalefnt}
\usepackage{algorithm}
\usepackage{algorithmic}
\pagestyle{empty}
\newcommand{\N}{\ensuremath{\mathbb{N}}}
\newcommand{\Z}{\ensuremath{\mathbb{Z}}}
\newcommand{\R}{\ensuremath{\mathbb{R}}}
\newcommand{\meet}{\ensuremath{\wedge}}
\newcommand{\Meet}{\ensuremath{\bigwedge}}
\newcommand{\join}{\ensuremath{\vee}}
\renewcommand{\emptyset}{\ensuremath{\varnothing}}
\renewcommand{\subset}{\ensuremath{\subsetneq}}
\newcommand{\boldemph}{\emph}
\newcommand{\lcm}{\operatorname{lcm}}

\begin{document}
\thispagestyle{empty}

\noindent \textbf{Math 3140 -- Homework 5} \hfill {\bf Due date:} Monday, 10/1\\[4pt]
\noindent {\bf Required Exercises.  Chapter 4:  6, 12, 13, 28, 30, 35}.

\begin{enumerate}

%% 6 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\item[{\bf 6.}]
Find the order of every element in the symmetry group of the square,
$D_4$.

\textbf{Answer:} The order of each element in $D_4$ is as follows:
\begin{itemize}
    \item The identity element has order 1.
    \item The rotations by 90 degrees and 270 degrees have order 4.
    \item The rotations by 180 degrees have order 2.
    \item The reflections have order 2.
\end{itemize}

\bigskip

%% 12 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\item[{\bf 12.}]
Find a cyclic group with exactly one generator.  Can you find cyclic
groups with exactly two generators?  Four generators?  How about $n$
generators?

\textbf{Answer:} 
\begin{itemize}
    \item A cyclic group with exactly one generator is the trivial group $\{e\}$.
    \item A cyclic group with exactly two generators is the group $\mathbb{Z}_2$ under addition.
    \item A cyclic group with exactly four generators is the group $\mathbb{Z}_4$ under addition.
    \item A cyclic group with $n$ generators is the group $\mathbb{Z}_n$ under addition.
\end{itemize}

\bigskip

%% 13 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\item[{\bf 13.}]
For $n \leq 20$, which groups $U(n)$ are cyclic?  Make a conjecture as
to what is true in general.  Can you prove your conjecture?  

\textbf{Answer:} For $n \leq 20$, the groups $U(n)$ are cyclic if and only if $n$ is one of the following: 1, 2, 4, a power of an odd prime, or twice a power of an odd prime. 

Conjecture: The group $U(n)$ is cyclic if and only if $n$ is 1, 2, 4, a power of an odd prime, or twice a power of an odd prime.

Proof: To prove this conjecture, we need to show that if $n$ is not of the specified form, then $U(n)$ is not cyclic. This can be done by providing a counterexample.